### 2013-05-08 doc/icml2013/theory.tex
Changed whitening lemma to express parameter error as epsilon. Also minor fixes

\begin{theorem}[Convergence of Spectral Experts]
\label{thm:convergence}
Assume each dataset $\sD_p$ (for $p = 1, 2, 3$) consists of $n$ i.i.d.\ points independently drawn from a mixture
of linear regressions model with parameter $\theta^*$.\footnote{Having three independent copies simplifies the analysis.}
Further, assume 
$\|x\|_2 \le R$, 
$\|\beta_h^*\|_2 \le L$ for all $h \in [k]$,
$|\epsilon| \le S$
and $B$ is rank $k$.
Let $\Sigma_p \eqdef \E[\cvec(x\tp{p})\tp{2}]$, 
and assume $\Sigma_p \succ 0$ for each $p \in \{1,2,3\}$.
Let $\epsilon$ be such that, 
$$\epsilon = O\left( \min\left\{ \frac{k\|M_3\|_\op \pi_{\max}}{\sigma_k(M_2)^{3/2}}, \half \right\}\right).$$ 
Suppose the number of samples is
$n = \max(n_1,n_2)$
where 
\begin{align*}
n_1 &= \Omega \left(\frac{R^{12} \log(1/\delta)}{\min_{p \in [3]} \sigmamin(\Sigma_p)^2} \right) \\
n_2 &= \Omega \left(\epsilon^{-2}~ \frac{k^2 \pi^2_{\max} \|M_3\|_\op^2}{\sigma_k(M_2)^{5} }\frac{ L^{6} S^{6} R^{12}}{\sigmamin(\Sigma_1)^2} \log(1/\delta) \right).
\end{align*}
If each regularization strength $\lambda_n^{(p)}$ is set to 
$$\Theta\left( L^p S^p R^{2p} \sqrt{\frac{\log(1/\delta)}{n}} \right),$$
for $p \in 2, 3$,
%$O\left(\frac{\sigmamin(\Sigma_p)}{\sqrt{k}}~ \epsilon \right)$, 
%$\Omega\left(\sigma^3 L^3 R^6 \sqrt{\frac{\log(1/\delta)}{n}}\right)$,
then the parameter estimates $\hat\theta = (\hat\pi, \hat B)$ returned by
\algorithmref{algo:spectral-experts} (with the columns appropriately permuted)
satisfies 
  \begin{align*}
  \|\hat \pi - \pi \|_{\infty} \le \epsilon \quad\quad 
  %&= O\left(\frac{k \pi_{\max}^{5/2}\| {M_3} \|_\op}{\sigma_k(M_2)^{5/2}} ~ \epsilon \right) \\
  \|\hat \beta_h - \beta_h\|_2 \le \epsilon
  %&= O\left( \frac{k \pi_{\max} \|M_2\|_\op^{1/2} \| {M_3} \|_\op}{\sigma_k(M_2)^{5/2}}~ \epsilon \right),
  \end{align*}
  for all $h \in [k]$.
%$\|\hat\pi - \pi^*\|_{\infty} \le \epsilon$
%and for all $h \in [k]$,
%$\|\hat\beta_h - \beta^*_h\|_2 \le \frac{\epsilon}{\sqrt{\pi_h^*}}$.
\end{theorem}

@@

Having bounded the error of the compound parameter estimates $\hat M_2$ and $\hat M_3$,
we will now study how this error propagates through the tensor factorization step of 
\algorithmref{algo:spectral-experts},
which includes whitening, applying the robust tensor power method \cite{AnandkumarGeHsu2012},
and unwhitening.
\begin{lemma}
  \label{lem:tensorPower} Let $\|\hat M_2 - M_2\|_\op \le \epsilon$ and
  $\|\hat M_3 - M_3\|_\op \le \epsilon$, for some $\epsilon$ in
  $$O\left( \min\left\{ 
    \frac{\sigma_k(M_2)}{2}, 
    \frac{\sigma_k(M_2)^{5/2}}{k \pi_{\max} \|M_3\|_\op} 
    \right\}\right).$$ 
  Then, there exists a permutation of indices such that  the parameter
  estimates found in step 2 of \algorithmref{algo:spectral-experts}
  satisfy the following with probability at least $1 - \delta$:
  \begin{align*}
  \|\hat \pi - \pi \|_{\infty}
  &= O\left(\frac{k \pi_{\max}^{5/2}\| {M_3} \|_\op}{\sigma_k(M_2)^{5/2}} ~ \epsilon \right) \\
  \|\hat \beta_h - \beta_h\|_2
  &= O\left( \frac{k \pi_{\max} \|M_2\|_\op^{1/2} \| {M_3} \|_\op}{ \sigma_k(M_2)^{5/2} }~ \epsilon \right),
  \end{align*}
  for all $h \in [k]$.
\end{lemma}

>>>>

\begin{theorem}[Convergence of Spectral Experts]
\label{thm:convergence}
Assume each dataset $\sD_p$ (for $p = 1, 2, 3$) consists of $n$ i.i.d.\ points independently drawn from a mixture
of linear regressions model with parameter $\theta^*$.\footnote{Having three independent copies simplifies the analysis.}
Further, assume 
$\|x\|_2 \le R$, 
$\|\beta_h^*\|_2 \le L$ for all $h \in [k]$,
$|\epsilon| \le S$
and $B$ is rank $k$.
Let $\Sigma_p \eqdef \E[\cvec(x\tp{p})\tp{2}]$, 
and assume $\Sigma_p \succ 0$ for each $p \in \{1,2,3\}$.
Let $\epsilon < \half$.
Suppose the number of samples is
$n = \max(n_1,n_2)$
where 
\begin{align*}
n_1 &= \Omega \left(\frac{R^{12} \log(1/\delta)}{\min_{p \in [3]} \sigmamin(\Sigma_p)^2} \right) \\
n_2 &= \Omega \left(\epsilon^{-2}~ \frac{k^2 \pi^2_{\max} \|M_2\|_\op^{1/2} \|M_3\|_\op^2 { L^{6} S^{6} R^{12}}}{\sigma_k(M_2)^{5} {\sigmamin(\Sigma_1)^2}} \log(1/\delta) \right).
\end{align*}
If each regularization strength $\lambda_n^{(p)}$ is set to 
$$\Theta\left( \frac{L^p S^p R^{2p}}{\sigmamin(\Sigma_1)^2} \sqrt{\frac{\log(1/\delta)}{n}} \right),$$
for $p \in 2, 3$,
%$O\left(\frac{\sigmamin(\Sigma_p)}{\sqrt{k}}~ \epsilon \right)$, 
%$\Omega\left(\sigma^3 L^3 R^6 \sqrt{\frac{\log(1/\delta)}{n}}\right)$,
then the parameter estimates $\hat\theta = (\hat\pi, \hat B)$ returned by
\algorithmref{algo:spectral-experts} (with the columns appropriately permuted)
satisfies 
  \begin{align*}
  \|\hat \pi - \pi \|_{\infty} \le \epsilon \quad\quad 
  %&= O\left(\frac{k \pi_{\max}^{5/2}\| {M_3} \|_\op}{\sigma_k(M_2)^{5/2}} ~ \epsilon \right) \\
  \|\hat \beta_h - \beta_h\|_2 \le \epsilon
  %&= O\left( \frac{k \pi_{\max} \|M_2\|_\op^{1/2} \| {M_3} \|_\op}{\sigma_k(M_2)^{5/2}}~ \epsilon \right),
  \end{align*}
  for all $h \in [k]$.
%$\|\hat\pi - \pi^*\|_{\infty} \le \epsilon$
%and for all $h \in [k]$,
%$\|\hat\beta_h - \beta^*_h\|_2 \le \frac{\epsilon}{\sqrt{\pi_h^*}}$.
\end{theorem}

@@

Having bounded the error of the compound parameter estimates $\hat M_2$ and $\hat M_3$,
we will now study how this error propagates through the tensor factorization step of 
\algorithmref{algo:spectral-experts},
which includes whitening, applying the robust tensor power method \cite{AnandkumarGeHsu2012},
and unwhitening.
\begin{lemma}
  \label{lem:tensorPower} Let $\|\hat M_2 - M_2\|_\op$ and $\|\hat M_3 - M_3\|_\op$ both be less than
  \vspace{-0.5em}
  $$\frac{\sigma_k(M_2)^{5/2}}{k \pi_{\max} \|M_2\|_\op^{1/2} \| {M_3} \|_\op}~ \epsilon,$$
  for some $\epsilon < \half$. 
  Then, there exists a permutation of indices such that  the parameter
  estimates found in step 2 of \algorithmref{algo:spectral-experts}
  satisfy the following with probability at least $1 - \delta$:
  \begin{align*}
  \|\hat \pi - \pi \|_{\infty} &\le \epsilon \\
  %&= O\left(\frac{k \pi_{\max}^{5/2}\| {M_3} \|_\op}{\sigma_k(M_2)^{5/2}} ~ \epsilon \right) \\
  \|\hat \beta_h - \beta_h\|_2 &\le \epsilon.
  %&= O\left( \frac{k \pi_{\max} \|M_2\|_\op^{1/2} \| {M_3} \|_\op}{ \sigma_k(M_2)^{5/2} }~ \epsilon \right),
  \end{align*}
  for all $h \in [k]$.
\end{lemma}
